Generate Real and Pseudo-absences

### 2023-12-18 scripts/generate_absences.Rmd
remove ocean from absence_drawer, keep distance same and increase absence density

```{r load packages}
library(tidyverse)
library(sf)
source('functions.R')
```

@@

@@

out <- lapply(records, absence_drawer, bg_abs = 0.15)
out <- bind_rows(out)
st_write(out, '../data/raw/occurrence/absences.shp')

ab <- st_read('../data/raw/occurrence/absences.shp')
```

@@

  LDA_model <- lda(Species ~ ., training) # generate model

>>>>

```{r load packages}
library(tidyverse)
library(sf)
library(terra)
source('functions.R')
```

@@

# here we subset a terrestrial surface to our area of analysis - we don't want all of
# our random points to fall in the ocean

domain <- rast(nrows = 1, ncols = 1) # create a big empty raster, you can go in through sf too. 
ext(domain) <- c( -125.5, -100, 27,  50) # set the extent
crs(domain) <- "EPSG:4326" # define the projection
domain <- as.polygons(domain) |>  # convert to vector data
  st_as_sf() |> # convert to simple feature
  st_bbox()

land <- rnaturalearth::ne_download(type= 'land', scale = 10, category= 'physical') |>
  sf::st_as_sf()
land <- st_crop(land, domain) |>
  st_transform(5070)

rm(domain)

@@

out <- lapply(records, absence_drawer, terrestrial = land,  bg_abs = 0.15)
out <- bind_rows(out)
st_write(out, '../data/raw/occurrence/absences.shp')

ab <- st_read('../data/raw/occurrence/absences.shp')

table(records$taxon)
```

@@

  LDA_model <- MASS::lda(Species ~ ., training) # generate model
